---
title: "Untitled"
output: html_document
date: "2024-12-11"
---

```{r}
library(surviplot)
library(beeswarm)

clin <- read.table('merged_cn_TCGA_survival_data.csv', sep=',', as.is=T, header=T, row.names=1)

```

```{r}
library(survival)
```


```{r}
stage_early_late.os_summary_results1 <- read.table('coxph/coxph.stage_early_late.os_summary_results1.csv', sep=',', as.is=T, header=T)
```


```{r}
clin <- clin[clin$ajcc_pathologic_tumor_stage != "[Not Available]", ]

```


#PFI.time and OS.time are converted to time by year.
```{r}
surv.pfi <- Surv(clin$PFI.time/365, clin$PFI)
surv.os <- Surv(clin$OS.time/365, clin$OS)

```



#test early late 2

```{r}
clin$ajcc_pathologic_tumor_stage_EL <- factor(ifelse(clin$ajcc_pathologic_tumor_stage %in% c("Stage III", "Stage IV"), 
                                                           "Late Stage", "Early Stage"))

```

```{r}
cox_model <- coxph(censor(surv.os,5) ~ tumor.45S + age_at_initial_pathologic_diagnosis + gender + ajcc_pathologic_tumor_stage_EL , data = clin)
summary(cox_model)
```
```{r}

library(survminer)
```



```{r}
# Plot grouped survival curves
fit <- survfit(cox_model, data = clin)
ggsurvplot(fit, data = clin,
           conf.int = TRUE,  # Show confidence intervals
           pval = TRUE,      # Display p-value
           risk.table = TRUE,# Show risk table
           ggtheme = theme_minimal(),
           title = "Survival Curves by Cox Model")
```





#test stage1 2 3 exclude stage1 coz only 1 for stage 1
```{r}
clin_stage <- clin
clin_stage <- clin[clin$ajcc_pathologic_tumor_stage != "Stage I", ]

```

```{r}
surv.pfi_stage <- Surv(clin_stage$PFI.time/365, clin_stage$PFI)
surv.os_stage <- Surv(clin_stage$OS.time/365, clin_stage$OS)

```


```{r}
cox_model_stage <- coxph(censor(surv.os_stage,5) ~ tumor.45S + age_at_initial_pathologic_diagnosis + gender + ajcc_pathologic_tumor_stage , data = clin_stage)
summary(cox_model_stage)
```


#all






#ajcc_pathologic_tumor_stage_EL pfi
```{r}
# Initialize dataframe to store results
cox_summary <- data.frame(
  Variable = character(),        # Covariate name
  Coefficient = numeric(),       # Regression coefficient
  Hazard_Ratio = numeric(),      # Hazard ratio
  SE = numeric(),                # Standard error
  z_value = numeric(),           # z value
  p_value = numeric(),           # p-value
  exp_neg_coef = numeric(),      # Inverse of hazard ratio
  lower_95 = numeric(),          # Lower 95% confidence interval
  upper_95 = numeric(),          # Upper 95% confidence interval
  Concordance = numeric(),       # Concordance index
  Likelihood_Ratio_Test = numeric(), # Likelihood ratio test
  Wald_Test = numeric(),         # Wald test
  Score_Test = numeric(),        # Score test
  stringsAsFactors = FALSE
)


# cn
for (i in 1:27) {
  #Get covariate name
  var_name <- colnames(clin)[i]
  #print(var_name)

  # formula
  formula <- as.formula(paste("censor(surv.pfi, 5) ~", var_name, "+ age_at_initial_pathologic_diagnosis + gender + ajcc_pathologic_tumor_stage_EL"))

  # coxph model
  cox_model <- coxph(formula, data = clin)
  cox_summary_temp <- summary(cox_model)

  # Extract the results of the main covariates
  main_var_row <- data.frame(
    Variable = var_name,
    Coefficient = cox_summary_temp$coefficients[1, "coef"],
    Hazard_Ratio = exp(cox_summary_temp$coefficients[1, "coef"]),
    SE = cox_summary_temp$coefficients[1, "se(coef)"],
    z_value = cox_summary_temp$coefficients[1, "z"],
    p_value = cox_summary_temp$coefficients[1, "Pr(>|z|)"],
    exp_neg_coef = exp(-cox_summary_temp$coefficients[1, "coef"]),
    lower_95 = cox_summary_temp$conf.int[1, "lower .95"],
    upper_95 = cox_summary_temp$conf.int[1, "upper .95"],
    Concordance = cox_summary_temp$concordance[1],
    Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
    Wald_Test = cox_summary_temp$waldtest[1],
    Score_Test = cox_summary_temp$sctest[1]
  )

  # # Extract the results of age
  age_row <- data.frame(
    Variable = "age_at_initial_pathologic_diagnosis",
    Coefficient = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"],
    Hazard_Ratio = exp(cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"]),
    SE = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "se(coef)"],
    z_value = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "z"],
    p_value = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "Pr(>|z|)"],
    exp_neg_coef = exp(-cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"]),
    lower_95 = cox_summary_temp$conf.int["age_at_initial_pathologic_diagnosis", "lower .95"],
    upper_95 = cox_summary_temp$conf.int["age_at_initial_pathologic_diagnosis", "upper .95"],
    Concordance = cox_summary_temp$concordance[1],
    Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
    Wald_Test = cox_summary_temp$waldtest[1],
    Score_Test = cox_summary_temp$sctest[1]
  )

  # Extract the results of gender
  gender_levels <- rownames(cox_summary_temp$coefficients)
  gender_row <- NULL
  if (any(grepl("gender", gender_levels))) {
    gender_row <- data.frame(
      Variable = "gender",
      Coefficient = cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"],
      Hazard_Ratio = exp(cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"]),
      SE = cox_summary_temp$coefficients[grepl("gender", gender_levels), "se(coef)"],
      z_value = cox_summary_temp$coefficients[grepl("gender", gender_levels), "z"],
      p_value = cox_summary_temp$coefficients[grepl("gender", gender_levels), "Pr(>|z|)"],
      exp_neg_coef = exp(-cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"]),
      lower_95 = cox_summary_temp$conf.int[grepl("gender", rownames(cox_summary_temp$conf.int)), "lower .95"],
      upper_95 = cox_summary_temp$conf.int[grepl("gender", rownames(cox_summary_temp$conf.int)), "upper .95"],
      Concordance = cox_summary_temp$concordance[1],
      Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
      Wald_Test = cox_summary_temp$waldtest[1],
      Score_Test = cox_summary_temp$sctest[1]
    )
  }

  # Extract the results of stage EL
  ajcc_levels <- rownames(cox_summary_temp$coefficients)
  ajcc_row <- NULL
  if (any(grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels))) {
    ajcc_row <- data.frame(
      Variable = "ajcc_pathologic_tumor_stage_EL",
      Coefficient = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "coef"],
      Hazard_Ratio = exp(cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "coef"]),
      SE = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "se(coef)"],
      z_value = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "z"],
      p_value = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "Pr(>|z|)"],
      exp_neg_coef = exp(-cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "coef"]),
      lower_95 = cox_summary_temp$conf.int[grepl("ajcc_pathologic_tumor_stage_EL", rownames(cox_summary_temp$conf.int)), "lower .95"],
      upper_95 = cox_summary_temp$conf.int[grepl("ajcc_pathologic_tumor_stage_EL", rownames(cox_summary_temp$conf.int)), "upper .95"],
      Concordance = cox_summary_temp$concordance[1],
      Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
      Wald_Test = cox_summary_temp$waldtest[1],
      Score_Test = cox_summary_temp$sctest[1]
    )
  }

  # combine
  cox_summary <- rbind(cox_summary, main_var_row, age_row, gender_row, ajcc_row)
}


#ratio blood/tumor 
# Extract the results for each covariate
for (i in seq(1, 18, by=2)) {
  #Get covariate name
  var_name <- paste(colnames(clin)[i+1], "/", colnames(clin)[i])
  #print(var_name)
  
  temp_data <- clin
  temp_data$new_var <- temp_data[[i+1]] / temp_data[[i]]  # 计算比值

  # formula
  formula <- as.formula(paste("censor(surv.pfi, 5) ~ new_var + age_at_initial_pathologic_diagnosis + gender + ajcc_pathologic_tumor_stage_EL"))

  # coxph model
  cox_model <- coxph(formula, data = temp_data)
  cox_summary_temp <- summary(cox_model)

  # Extract the results of the main covariates
  main_var_row <- data.frame(
    Variable = var_name,
    Coefficient = cox_summary_temp$coefficients[1, "coef"],
    Hazard_Ratio = exp(cox_summary_temp$coefficients[1, "coef"]),
    SE = cox_summary_temp$coefficients[1, "se(coef)"],
    z_value = cox_summary_temp$coefficients[1, "z"],
    p_value = cox_summary_temp$coefficients[1, "Pr(>|z|)"],
    exp_neg_coef = exp(-cox_summary_temp$coefficients[1, "coef"]),
    lower_95 = cox_summary_temp$conf.int[1, "lower .95"],
    upper_95 = cox_summary_temp$conf.int[1, "upper .95"],
    Concordance = cox_summary_temp$concordance[1],
    Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
    Wald_Test = cox_summary_temp$waldtest[1],
    Score_Test = cox_summary_temp$sctest[1]
  )

  #Extract the results of age
  age_row <- data.frame(
    Variable = "age_at_initial_pathologic_diagnosis",
    Coefficient = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"],
    Hazard_Ratio = exp(cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"]),
    SE = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "se(coef)"],
    z_value = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "z"],
    p_value = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "Pr(>|z|)"],
    exp_neg_coef = exp(-cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"]),
    lower_95 = cox_summary_temp$conf.int["age_at_initial_pathologic_diagnosis", "lower .95"],
    upper_95 = cox_summary_temp$conf.int["age_at_initial_pathologic_diagnosis", "upper .95"],
    Concordance = cox_summary_temp$concordance[1],
    Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
    Wald_Test = cox_summary_temp$waldtest[1],
    Score_Test = cox_summary_temp$sctest[1]
  )

  # Extract the results of gender
  gender_levels <- rownames(cox_summary_temp$coefficients)
  gender_row <- NULL
  if (any(grepl("gender", gender_levels))) {
    gender_row <- data.frame(
      Variable = "gender",
      Coefficient = cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"],
      Hazard_Ratio = exp(cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"]),
      SE = cox_summary_temp$coefficients[grepl("gender", gender_levels), "se(coef)"],
      z_value = cox_summary_temp$coefficients[grepl("gender", gender_levels), "z"],
      p_value = cox_summary_temp$coefficients[grepl("gender", gender_levels), "Pr(>|z|)"],
      exp_neg_coef = exp(-cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"]),
      lower_95 = cox_summary_temp$conf.int[grepl("gender", rownames(cox_summary_temp$conf.int)), "lower .95"],
      upper_95 = cox_summary_temp$conf.int[grepl("gender", rownames(cox_summary_temp$conf.int)), "upper .95"],
      Concordance = cox_summary_temp$concordance[1],
      Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
      Wald_Test = cox_summary_temp$waldtest[1],
      Score_Test = cox_summary_temp$sctest[1]
    )
  }

  # Extract the results of stage EL
  ajcc_levels <- rownames(cox_summary_temp$coefficients)
  ajcc_row <- NULL
  if (any(grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels))) {
    ajcc_row <- data.frame(
      Variable = "ajcc_pathologic_tumor_stage_EL",
      Coefficient = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "coef"],
      Hazard_Ratio = exp(cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "coef"]),
      SE = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "se(coef)"],
      z_value = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "z"],
      p_value = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "Pr(>|z|)"],
      exp_neg_coef = exp(-cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "coef"]),
      lower_95 = cox_summary_temp$conf.int[grepl("ajcc_pathologic_tumor_stage_EL", rownames(cox_summary_temp$conf.int)), "lower .95"],
      upper_95 = cox_summary_temp$conf.int[grepl("ajcc_pathologic_tumor_stage_EL", rownames(cox_summary_temp$conf.int)), "upper .95"],
      Concordance = cox_summary_temp$concordance[1],
      Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
      Wald_Test = cox_summary_temp$waldtest[1],
      Score_Test = cox_summary_temp$sctest[1]
    )
  }

  # combine
  cox_summary <- rbind(cox_summary, main_var_row, age_row, gender_row, ajcc_row)
}

#ratio blood/tumor without correction
# Extract the results for each covariate
for (i in seq(1, 18, by = 2)) {
  #Get covariate name
  var_name <- paste(colnames(clin)[((i + 1) / 2 + 18)], "/", colnames(clin)[i])
  #print(var_name)
  
  temp_data <- clin
  temp_data$new_var <- as.numeric(temp_data[[((i + 1) / 2 + 18)]]) / as.numeric(temp_data[[i]])  

  # formula
  formula <- as.formula(paste("censor(surv.pfi, 5) ~ new_var + age_at_initial_pathologic_diagnosis + gender + ajcc_pathologic_tumor_stage_EL"))

  # coxph model
  cox_model <- coxph(formula, data = temp_data)
  cox_summary_temp <- summary(cox_model)

  # Extract the results of the main covariates
  main_var_row <- data.frame(
    Variable = var_name,
    Coefficient = cox_summary_temp$coefficients[1, "coef"],
    Hazard_Ratio = exp(cox_summary_temp$coefficients[1, "coef"]),
    SE = cox_summary_temp$coefficients[1, "se(coef)"],
    z_value = cox_summary_temp$coefficients[1, "z"],
    p_value = cox_summary_temp$coefficients[1, "Pr(>|z|)"],
    exp_neg_coef = exp(-cox_summary_temp$coefficients[1, "coef"]),
    lower_95 = cox_summary_temp$conf.int[1, "lower .95"],
    upper_95 = cox_summary_temp$conf.int[1, "upper .95"],
    Concordance = cox_summary_temp$concordance[1],
    Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
    Wald_Test = cox_summary_temp$waldtest[1],
    Score_Test = cox_summary_temp$sctest[1]
  )

  # # Extract the results of age
  age_row <- data.frame(
    Variable = "age_at_initial_pathologic_diagnosis",
    Coefficient = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"],
    Hazard_Ratio = exp(cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"]),
    SE = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "se(coef)"],
    z_value = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "z"],
    p_value = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "Pr(>|z|)"],
    exp_neg_coef = exp(-cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"]),
    lower_95 = cox_summary_temp$conf.int["age_at_initial_pathologic_diagnosis", "lower .95"],
    upper_95 = cox_summary_temp$conf.int["age_at_initial_pathologic_diagnosis", "upper .95"],
    Concordance = cox_summary_temp$concordance[1],
    Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
    Wald_Test = cox_summary_temp$waldtest[1],
    Score_Test = cox_summary_temp$sctest[1]
  )

  # Extract the results of gender
  gender_levels <- rownames(cox_summary_temp$coefficients)
  gender_row <- NULL
  if (any(grepl("gender", gender_levels))) {
    gender_row <- data.frame(
      Variable = "gender",
      Coefficient = cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"],
      Hazard_Ratio = exp(cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"]),
      SE = cox_summary_temp$coefficients[grepl("gender", gender_levels), "se(coef)"],
      z_value = cox_summary_temp$coefficients[grepl("gender", gender_levels), "z"],
      p_value = cox_summary_temp$coefficients[grepl("gender", gender_levels), "Pr(>|z|)"],
      exp_neg_coef = exp(-cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"]),
      lower_95 = cox_summary_temp$conf.int[grepl("gender", rownames(cox_summary_temp$conf.int)), "lower .95"],
      upper_95 = cox_summary_temp$conf.int[grepl("gender", rownames(cox_summary_temp$conf.int)), "upper .95"],
      Concordance = cox_summary_temp$concordance[1],
      Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
      Wald_Test = cox_summary_temp$waldtest[1],
      Score_Test = cox_summary_temp$sctest[1]
    )
  }

  # Extract the results of stage EL
  ajcc_levels <- rownames(cox_summary_temp$coefficients)
  ajcc_row <- NULL
  if (any(grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels))) {
    ajcc_row <- data.frame(
      Variable = "ajcc_pathologic_tumor_stage_EL",
      Coefficient = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "coef"],
      Hazard_Ratio = exp(cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "coef"]),
      SE = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "se(coef)"],
      z_value = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "z"],
      p_value = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "Pr(>|z|)"],
      exp_neg_coef = exp(-cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "coef"]),
      lower_95 = cox_summary_temp$conf.int[grepl("ajcc_pathologic_tumor_stage_EL", rownames(cox_summary_temp$conf.int)), "lower .95"],
      upper_95 = cox_summary_temp$conf.int[grepl("ajcc_pathologic_tumor_stage_EL", rownames(cox_summary_temp$conf.int)), "upper .95"],
      Concordance = cox_summary_temp$concordance[1],
      Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
      Wald_Test = cox_summary_temp$waldtest[1],
      Score_Test = cox_summary_temp$sctest[1]
    )
  }

  # combine
  cox_summary <- rbind(cox_summary, main_var_row, age_row, gender_row, ajcc_row)
}





# save
write.csv(cox_summary, "coxph/coxph.stage_early_late.pfi_summary_results1.csv", row.names = FALSE)



print(cox_summary)
```






#ajcc_pathologic_tumor_stage_EL os
```{r}
# Initialize the data frame that holds the results
cox_summary <- data.frame(
  Variable = character(), # covariate name
  Coefficient = numeric(), # Regression coefficient
  Hazard_Ratio = numeric(), # Risk ratio
  SE = numeric(), # Standard Error
  z_value = numeric(), # z value
  p_value = numeric(), # p value
  exp_neg_coef = numeric(), # inverse risk ratio
  lower_95 = numeric(), # Lower bound of 95% confidence interval
  upper_95 = numeric(), # 95% confidence interval upper bound
  Concordance = numeric(), # Consistency index
  Likelihood_Ratio_Test = numeric(), # Likelihood ratio test
  Wald_Test = numeric(), # Wald test
  Score_Test = numeric(), # Score test
  stringsAsFactors = FALSE
)


# cn
for (i in 1:27) {
  #Get covariate name
  var_name <- colnames(clin)[i]
  #print(var_name)

  # formula
  formula <- as.formula(paste("censor(surv.os, 5) ~", var_name, "+ age_at_initial_pathologic_diagnosis + gender + ajcc_pathologic_tumor_stage_EL"))

  # coxph model
  cox_model <- coxph(formula, data = clin)
  cox_summary_temp <- summary(cox_model)

  # Extract the results of the main covariates
  main_var_row <- data.frame(
    Variable = var_name,
    Coefficient = cox_summary_temp$coefficients[1, "coef"],
    Hazard_Ratio = exp(cox_summary_temp$coefficients[1, "coef"]),
    SE = cox_summary_temp$coefficients[1, "se(coef)"],
    z_value = cox_summary_temp$coefficients[1, "z"],
    p_value = cox_summary_temp$coefficients[1, "Pr(>|z|)"],
    exp_neg_coef = exp(-cox_summary_temp$coefficients[1, "coef"]),
    lower_95 = cox_summary_temp$conf.int[1, "lower .95"],
    upper_95 = cox_summary_temp$conf.int[1, "upper .95"],
    Concordance = cox_summary_temp$concordance[1],
    Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
    Wald_Test = cox_summary_temp$waldtest[1],
    Score_Test = cox_summary_temp$sctest[1]
  )

  # # Extract the results of age
  age_row <- data.frame(
    Variable = "age_at_initial_pathologic_diagnosis",
    Coefficient = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"],
    Hazard_Ratio = exp(cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"]),
    SE = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "se(coef)"],
    z_value = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "z"],
    p_value = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "Pr(>|z|)"],
    exp_neg_coef = exp(-cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"]),
    lower_95 = cox_summary_temp$conf.int["age_at_initial_pathologic_diagnosis", "lower .95"],
    upper_95 = cox_summary_temp$conf.int["age_at_initial_pathologic_diagnosis", "upper .95"],
    Concordance = cox_summary_temp$concordance[1],
    Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
    Wald_Test = cox_summary_temp$waldtest[1],
    Score_Test = cox_summary_temp$sctest[1]
  )

  # Extract the results of gender
  gender_levels <- rownames(cox_summary_temp$coefficients)
  gender_row <- NULL
  if (any(grepl("gender", gender_levels))) {
    gender_row <- data.frame(
      Variable = "gender",
      Coefficient = cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"],
      Hazard_Ratio = exp(cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"]),
      SE = cox_summary_temp$coefficients[grepl("gender", gender_levels), "se(coef)"],
      z_value = cox_summary_temp$coefficients[grepl("gender", gender_levels), "z"],
      p_value = cox_summary_temp$coefficients[grepl("gender", gender_levels), "Pr(>|z|)"],
      exp_neg_coef = exp(-cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"]),
      lower_95 = cox_summary_temp$conf.int[grepl("gender", rownames(cox_summary_temp$conf.int)), "lower .95"],
      upper_95 = cox_summary_temp$conf.int[grepl("gender", rownames(cox_summary_temp$conf.int)), "upper .95"],
      Concordance = cox_summary_temp$concordance[1],
      Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
      Wald_Test = cox_summary_temp$waldtest[1],
      Score_Test = cox_summary_temp$sctest[1]
    )
  }

  # Extract the results of stage EL
  ajcc_levels <- rownames(cox_summary_temp$coefficients)
  ajcc_row <- NULL
  if (any(grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels))) {
    ajcc_row <- data.frame(
      Variable = "ajcc_pathologic_tumor_stage_EL",
      Coefficient = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "coef"],
      Hazard_Ratio = exp(cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "coef"]),
      SE = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "se(coef)"],
      z_value = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "z"],
      p_value = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "Pr(>|z|)"],
      exp_neg_coef = exp(-cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage_EL", ajcc_levels), "coef"]),
      lower_95 = cox_summary_temp$conf.int[grepl("ajcc_pathologic_tumor_stage_EL", rownames(cox_summary_temp$conf.int)), "lower .95"],
      upper_95 = cox_summary_temp$conf.int[grepl("ajcc_pathologic_tumor_stage_EL", rownames(cox_summary_temp$conf.int)), "upper .95"],
      Concordance = cox_summary_temp$concordance[1],
      Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
      Wald_Test = cox_summary_temp$waldtest[1],
      Score_Test = cox_summary_temp$sctest[1]
    )
  }

  # combine
  cox_summary <- rbind(cox_summary, main_var_row, age_row, gender_row, ajcc_row)
}





#ajcc_pathologic_tumor_stage pfi
```{r}
# Initialize the data frame that holds the results
cox_summary <- data.frame(
  Variable = character(), # covariate name
  Coefficient = numeric(), # Regression coefficient
  Hazard_Ratio = numeric(), # Risk ratio
  SE = numeric(), # Standard Error
  z_value = numeric(), # z value
  p_value = numeric(), # p value
  exp_neg_coef = numeric(), # inverse risk ratio
  lower_95 = numeric(), # Lower bound of 95% confidence interval
  upper_95 = numeric(), # 95% confidence interval upper bound
  Concordance = numeric(), # Consistency index
  Likelihood_Ratio_Test = numeric(), # Likelihood ratio test
  Wald_Test = numeric(), # Wald test
  Score_Test = numeric(), # Score test
  stringsAsFactors = FALSE
)


# cn
for (i in 1:27) {
  #Get covariate name
  var_name <- colnames(clin)[i]
  #print(var_name)

  # formula
  formula <- as.formula(paste("censor(surv.pfi_stage, 5) ~", var_name, "+ age_at_initial_pathologic_diagnosis + gender + ajcc_pathologic_tumor_stage"))

  # coxph model
  cox_model <- coxph(formula, data = clin_stage)
  cox_summary_temp <- summary(cox_model)

  # Extract the results of the main covariates
  main_var_row <- data.frame(
    Variable = var_name,
    Coefficient = cox_summary_temp$coefficients[1, "coef"],
    Hazard_Ratio = exp(cox_summary_temp$coefficients[1, "coef"]),
    SE = cox_summary_temp$coefficients[1, "se(coef)"],
    z_value = cox_summary_temp$coefficients[1, "z"],
    p_value = cox_summary_temp$coefficients[1, "Pr(>|z|)"],
    exp_neg_coef = exp(-cox_summary_temp$coefficients[1, "coef"]),
    lower_95 = cox_summary_temp$conf.int[1, "lower .95"],
    upper_95 = cox_summary_temp$conf.int[1, "upper .95"],
    Concordance = cox_summary_temp$concordance[1],
    Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
    Wald_Test = cox_summary_temp$waldtest[1],
    Score_Test = cox_summary_temp$sctest[1]
  )

  # # Extract the results of age
  age_row <- data.frame(
    Variable = "age_at_initial_pathologic_diagnosis",
    Coefficient = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"],
    Hazard_Ratio = exp(cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"]),
    SE = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "se(coef)"],
    z_value = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "z"],
    p_value = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "Pr(>|z|)"],
    exp_neg_coef = exp(-cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"]),
    lower_95 = cox_summary_temp$conf.int["age_at_initial_pathologic_diagnosis", "lower .95"],
    upper_95 = cox_summary_temp$conf.int["age_at_initial_pathologic_diagnosis", "upper .95"],
    Concordance = cox_summary_temp$concordance[1],
    Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
    Wald_Test = cox_summary_temp$waldtest[1],
    Score_Test = cox_summary_temp$sctest[1]
  )

  # Extract the results of gender
  gender_levels <- rownames(cox_summary_temp$coefficients)
  gender_row <- NULL
  if (any(grepl("gender", gender_levels))) {
    gender_row <- data.frame(
      Variable = "gender",
      Coefficient = cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"],
      Hazard_Ratio = exp(cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"]),
      SE = cox_summary_temp$coefficients[grepl("gender", gender_levels), "se(coef)"],
      z_value = cox_summary_temp$coefficients[grepl("gender", gender_levels), "z"],
      p_value = cox_summary_temp$coefficients[grepl("gender", gender_levels), "Pr(>|z|)"],
      exp_neg_coef = exp(-cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"]),
      lower_95 = cox_summary_temp$conf.int[grepl("gender", rownames(cox_summary_temp$conf.int)), "lower .95"],
      upper_95 = cox_summary_temp$conf.int[grepl("gender", rownames(cox_summary_temp$conf.int)), "upper .95"],
      Concordance = cox_summary_temp$concordance[1],
      Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
      Wald_Test = cox_summary_temp$waldtest[1],
      Score_Test = cox_summary_temp$sctest[1]
    )
  }

  # extract AJCC
  ajcc_levels <- rownames(cox_summary_temp$coefficients)
  ajcc_row <- NULL
  if (any(grepl("ajcc_pathologic_tumor_stage", ajcc_levels))) {
    ajcc_row <- data.frame(
      Variable = "ajcc_pathologic_tumor_stage",
      Coefficient = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage", ajcc_levels), "coef"],
      Hazard_Ratio = exp(cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage", ajcc_levels), "coef"]),
      SE = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage", ajcc_levels), "se(coef)"],
      z_value = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage", ajcc_levels), "z"],
      p_value = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage", ajcc_levels), "Pr(>|z|)"],
      exp_neg_coef = exp(-cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage", ajcc_levels), "coef"]),
      lower_95 = cox_summary_temp$conf.int[grepl("ajcc_pathologic_tumor_stage", rownames(cox_summary_temp$conf.int)), "lower .95"],
      upper_95 = cox_summary_temp$conf.int[grepl("ajcc_pathologic_tumor_stage", rownames(cox_summary_temp$conf.int)), "upper .95"],
      Concordance = cox_summary_temp$concordance[1],
      Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
      Wald_Test = cox_summary_temp$waldtest[1],
      Score_Test = cox_summary_temp$sctest[1]
    )
  }

  # combine
  cox_summary <- rbind(cox_summary, main_var_row, age_row, gender_row, ajcc_row)
}






#ajcc_pathologic_tumor_stage os
```{r}
# Initialize the data frame that holds the results
cox_summary <- data.frame(
  Variable = character(), # covariate name
  Coefficient = numeric(), # Regression coefficient
  Hazard_Ratio = numeric(), # Risk ratio
  SE = numeric(), # Standard Error
  z_value = numeric(), # z value
  p_value = numeric(), # p value
  exp_neg_coef = numeric(), # inverse risk ratio
  lower_95 = numeric(), # Lower bound of 95% confidence interval
  upper_95 = numeric(), # 95% confidence interval upper bound
  Concordance = numeric(), # Consistency index
  Likelihood_Ratio_Test = numeric(), # Likelihood ratio test
  Wald_Test = numeric(), # Wald test
  Score_Test = numeric(), # Score test
  stringsAsFactors = FALSE
)

# cn
for (i in 1:27) {
  #Get covariate name
  var_name <- colnames(clin)[i]
  #print(var_name)

  # formula
  formula <- as.formula(paste("censor(surv.os_stage, 5) ~", var_name, "+ age_at_initial_pathologic_diagnosis + gender + ajcc_pathologic_tumor_stage"))

  # coxph model
  cox_model <- coxph(formula, data = clin_stage)
  cox_summary_temp <- summary(cox_model)

  # Extract the results of the main covariates
  main_var_row <- data.frame(
    Variable = var_name,
    Coefficient = cox_summary_temp$coefficients[1, "coef"],
    Hazard_Ratio = exp(cox_summary_temp$coefficients[1, "coef"]),
    SE = cox_summary_temp$coefficients[1, "se(coef)"],
    z_value = cox_summary_temp$coefficients[1, "z"],
    p_value = cox_summary_temp$coefficients[1, "Pr(>|z|)"],
    exp_neg_coef = exp(-cox_summary_temp$coefficients[1, "coef"]),
    lower_95 = cox_summary_temp$conf.int[1, "lower .95"],
    upper_95 = cox_summary_temp$conf.int[1, "upper .95"],
    Concordance = cox_summary_temp$concordance[1],
    Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
    Wald_Test = cox_summary_temp$waldtest[1],
    Score_Test = cox_summary_temp$sctest[1]
  )

  # # Extract the results of age
  age_row <- data.frame(
    Variable = "age_at_initial_pathologic_diagnosis",
    Coefficient = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"],
    Hazard_Ratio = exp(cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"]),
    SE = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "se(coef)"],
    z_value = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "z"],
    p_value = cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "Pr(>|z|)"],
    exp_neg_coef = exp(-cox_summary_temp$coefficients["age_at_initial_pathologic_diagnosis", "coef"]),
    lower_95 = cox_summary_temp$conf.int["age_at_initial_pathologic_diagnosis", "lower .95"],
    upper_95 = cox_summary_temp$conf.int["age_at_initial_pathologic_diagnosis", "upper .95"],
    Concordance = cox_summary_temp$concordance[1],
    Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
    Wald_Test = cox_summary_temp$waldtest[1],
    Score_Test = cox_summary_temp$sctest[1]
  )

  # Extract the results of gender
  gender_levels <- rownames(cox_summary_temp$coefficients)
  gender_row <- NULL
  if (any(grepl("gender", gender_levels))) {
    gender_row <- data.frame(
      Variable = "gender",
      Coefficient = cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"],
      Hazard_Ratio = exp(cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"]),
      SE = cox_summary_temp$coefficients[grepl("gender", gender_levels), "se(coef)"],
      z_value = cox_summary_temp$coefficients[grepl("gender", gender_levels), "z"],
      p_value = cox_summary_temp$coefficients[grepl("gender", gender_levels), "Pr(>|z|)"],
      exp_neg_coef = exp(-cox_summary_temp$coefficients[grepl("gender", gender_levels), "coef"]),
      lower_95 = cox_summary_temp$conf.int[grepl("gender", rownames(cox_summary_temp$conf.int)), "lower .95"],
      upper_95 = cox_summary_temp$conf.int[grepl("gender", rownames(cox_summary_temp$conf.int)), "upper .95"],
      Concordance = cox_summary_temp$concordance[1],
      Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
      Wald_Test = cox_summary_temp$waldtest[1],
      Score_Test = cox_summary_temp$sctest[1]
    )
  }

  # 提取固定协变量 ajcc_pathologic_tumor 的结果
  ajcc_levels <- rownames(cox_summary_temp$coefficients)
  ajcc_row <- NULL
  if (any(grepl("ajcc_pathologic_tumor_stage", ajcc_levels))) {
    ajcc_row <- data.frame(
      Variable = "ajcc_pathologic_tumor_stage",
      Coefficient = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage", ajcc_levels), "coef"],
      Hazard_Ratio = exp(cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage", ajcc_levels), "coef"]),
      SE = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage", ajcc_levels), "se(coef)"],
      z_value = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage", ajcc_levels), "z"],
      p_value = cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage", ajcc_levels), "Pr(>|z|)"],
      exp_neg_coef = exp(-cox_summary_temp$coefficients[grepl("ajcc_pathologic_tumor_stage", ajcc_levels), "coef"]),
      lower_95 = cox_summary_temp$conf.int[grepl("ajcc_pathologic_tumor_stage", rownames(cox_summary_temp$conf.int)), "lower .95"],
      upper_95 = cox_summary_temp$conf.int[grepl("ajcc_pathologic_tumor_stage", rownames(cox_summary_temp$conf.int)), "upper .95"],
      Concordance = cox_summary_temp$concordance[1],
      Likelihood_Ratio_Test = cox_summary_temp$logtest[1],
      Wald_Test = cox_summary_temp$waldtest[1],
      Score_Test = cox_summary_temp$sctest[1]
    )
  }

  # combine
  cox_summary <- rbind(cox_summary, main_var_row, age_row, gender_row, ajcc_row)
}







# save
write.csv(cox_summary, "coxph/coxph.stage123.os_summary_results.csv", row.names = FALSE)



print(cox_summary)
```

